---
title: "Groups"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
library(tidyverse)
library(knitr)
library(kableExtra)
```

## Assignment 2 Peer Evaluation

In the table below you will find your student number and link to a zip
file containing another groups project. Your task is to try and reproduce
the other groups analysis, and read over their project. There will be a
quiz for you to respond to on ED during the class on 27th May. 

```{r setup-pe, eval = FALSE, echo = FALSE}
active_participants <- read_csv("active.csv", na = "-") %>% 
  janitor::clean_names() %>% 
  filter(!is.na(quiz_mida_midsemester_test_percentage)) %>% 
  select(monash_id = id_number)

library(googlesheets4)
gradebook <- "https://docs.google.com/spreadsheets/d/1C9RZRbD5sCzT6c4OhELdyTaBPCgtKQzX66CuFzUvUxg/edit?usp=sharing"
group_pe <- read_sheet(gradebook, 1) %>% 
  select(monash_id, group_name) %>% 
  filter(!is.na(group_name)) %>% 
  mutate(
    group_name = if_else(group_name == "tibble", "WeRTidy", group_name),
    group_name = if_else(group_name == "rmarkdown", "flowers", group_name)
  ) %>% 
  inner_join(active_participants)

zipfiles <- list.files("./assignments/peer-evaluation/", pattern = ".zip$")

set.seed(5510)
group_pe <- group_pe %>% 
  mutate(
    to_group = sample(group_name), # shuffle
    to_group = if_else(group_name == to_group, sample(to_group),  to_group)
  ) %>% 
  rename(from_group = group_name)

# check sampling worked
group_pe %>% filter(from_group == to_group)

write_csv(group_pe, here::here("assignments", "peer-evaluation.csv"))
```

```{r display-pe-groups, echo = FALSE}
read_csv(here::here("assignments", "peer-evaluation.csv")) %>% 
  mutate(zip = paste0("[", to_group, "](assignments/peer-evaluation/", to_group, ".zip)")) %>% 
  select(monash_id, peer_evaluate_group = zip) %>% 
  kable(escape = FALSE, align = c("l", "l")) %>% 
  kable_styling(bootstrap_options = "striped", fixed_thead = T) %>% 
  column_spec(1, width = "1cm") %>% 
  column_spec(2, width = "1cm") 
```

## Project groups

In the table below you will find your project group name, along with each member's student email. 

Please check this for correctness and email any mistakes to the course email address.

```{r display-groups, echo = FALSE}
read_csv(here::here("project", "project-groups.csv"),
         col_names = FALSE) %>% 
  rename(group = X1) %>% 
  pivot_longer(cols = -group, values_to = "email") %>% 
  filter(!is.na(email)) %>%
  select(-name) %>% 
  kable(escape = FALSE, 
        align = c("l", "l")) %>% 
  kable_styling(bootstrap_options = "striped", fixed_thead = TRUE) %>% 
  column_spec(1, width = "1cm") %>% 
  column_spec(2, width = "1cm")
```