---
title: "Making A Dashboard with flexdashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
```


Overview 
=======================================================================

Column
-----------------------------

```{r, echo = FALSE, fig.align="centre", out.width = "100%", }
xhrt <- function(t) 16*sin(t)^3
yhrt <- function(t) 13*cos(t)-5*cos(2*t)-2*cos(3*t)-cos(4*t)
frame <- tibble(t=seq(0, 2*pi, length.out=100),
                x = xhrt(t),
                y = yhrt(t))

ggplot(frame, aes(x = x, y = y)) + 
  geom_polygon(fill = "lightpink") +
  geom_text(aes(x = mean(x), y = mean(y), label = "DATA"), 
            color = "grey90",
            size = 18) +
  theme_void()
```


Column {.tabset}
------------------------------

### What's required to make a dashboard?

A dashboard is a way of communicating the output of data analysis to an audience, 
who may not be familiar with the intricate details of your data or the findings 
of your analysis but need to understand what you've done. 

You could think of a dashboard as an interactive story: it should provide a big picture overview of what the data shows, while allowing the user to interrogate specifics that they are interested. The dashboard should guide the 
user through your analysis and highlight details and findings you want them to understand. 

### What's required?

Before embarking on constructing a dashboard, you should have a pretty good
idea about your data: most of the wrangling and cleaning would be finished,
and models should be precomputed and saved, and an idea of what
visualisations you would like to show. The code you write to make a dashboard,
will mostly involve reshaping your data to make plots, that allow for 
visualisations.


### Design goals

1. at lest two inputs that a user can select or change things in the display 
1. at least one  interactive plot 
1. one user interface element containing modeling
1. a separate tab with description of the methodology, 


Data 
=======================================================================

Column {data-width=500}
------------------------------------

### How does my daily electricity usage change over time?

Our data is smart meter electricity usage, we have kilowatt per hour
usage measured for one household over a couple of years. 
We have also joined weather information for each day of the year to the
smart meter measurements and have saved the results to a tidy data.frame:

```{r}
elec_all <- read_rds("data/elec_all.rds")
elec_all
```


### Making a model and predictions 

We also fitted a linear model to this data, the model is a little complicated
but for the purposes of making a dashboard, we are interesting in showing
predictions from it.

```{r}
fit <- read_rds("data/model_fit.rds")
summary(fit)
```
