---
title: "ETC5510 Practical exam S1 2020"
author: "Your Name Here"
output: 
  html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.height = 8,
  fig.width = 12,
  fig.align = "center",
  cache = FALSE
)
```

# Expectations for independent work

COVID19 has meant that we've had to change a lot about how we teach and do the course. We wanted to give you all a fair opportunity to complete the assignment in a timeline that suits you. So we have given you 24 hours to complete the exam.

Please make sure that you don't cheat, and be fair. Penalties for cheating will carry the same academic penalty

- Open book
- Internet access
- No contacting / messaging / communicating friends during exam (penalty will be the same as cheating in exam)
- No collaborating with others (students, anyone online)
- No discussion on anything related to this exercise with others, the work submitted should reflect entirely your own work.
- Clarification questions can be asked between 12-2pm on Wednesday at the lecture zoom chat

# Due date

- Practical exam is worth 20% of your final grade
-  Rmd and HTML files have to be submitted on ED (7 possible marks)

- Practical exam opens at **6:00pm on Wednesday 3rd June**
- Practical exam closes at **6:00pm on Thursday 4th June**

# Marks

- 37 marks total
  - 7 Marks for submitting an Rmd document that compiles to HTML will full answers
  - 30 Marks for completing the ED quiz, which will contain the questions from the Rmd.
    - These questions will be multiple choice or short answer.

# Hand in

Turn in your Rmd and html output into ED as you have done for assignments.

# How to "turn off" code chunks

Your rmarkdown document will not compile if there are parts of code that don't work. You can set certain code chunks to not evaluate by setting `eval = FALSE`, like so:

```{r broken-code, eval = FALSE}
# This isn't marked, this is an example of how to set the code chunk
# to not evaluate by setting `eval = FALSE` as above.
ggplot(___) +
  geom____
```

# Exercise

```{r pkgs}
library(tidyverse)
library(lubridate)
```

# About the data

The COVID-19 pandemic has affected this semester of study, and how we currently live. This exercise will be to examine the data on COVID-19 incidence around the world. 

- COVID-19 incidence: There are numerous sources of incidence data, and we will look at one of the [COVID-19 Data Repository by the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University](https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv)

- State population data for Australia can be found at  https://en.wikipedia.org/wiki/List_of_Australian_states_and_territories_by_gross_state_product, and loaded using:

- Detailed data for Australia is available in the file, "australia.csv" 

Here is what each of the columns in the dataset contain

- Date, as date information
- State, each state of Australia
- Count - cumulative count of covid19
- deaths - cumulative deaths from covid19
- recovered - cumulative recoveries from covid19
- tested - cumulative count of those tested of covid19

```{r read-oz}
oz_covid19 <- read_csv("australia.csv") %>% mutate(date = ymd(date)) 
```

# 1. (1pt) What was the earliest and latest dates of Australian COVID-19 incidence in the data provided?

```{r earliest-latest-answer-student-copy}
# find the earliest and latest dates from `oz_covid19`
```

!> Answer: 

# 2. (1pt) How many different states and territories are represented in this data? 

```{r different-states-student-copy}
# What is the number of different states and territories in the data?
oz_covid19
```

!> Answer: 

# 3. (2pts)  Make a plot of the cumulative COVID-19 incidence in Victoria over the time period of the data.

```{r plot-cumulative-incidence-vic-student-copy}
# filter data to only include victoria
oz_covid19_vic <- oz_covid19 %>% ___

# Make a plot of the cumulative COVID-19 incidence in Victoria over the time period of the data.
ggplot(___,
       aes(x = ___,
           y = ___)) +
  geom_col()
```

!> Answer: 

# 4. From cumulative to daily (3 pts) 

## (a) Compute the daily counts from the cumulative counts, and 
## (b) Compute the daily recovered counts from the cumulative recovered counts

```{r compute-daily-counts-student-copy}
oz_covid19_daily <- ___ %>% 
  # group by state
  ___ %>% 
  # arrange by date
  ___ %>% 
  # create a column that contains the lagged counts of cases
  # look at `?dplyr::lag`
  mutate(lag_counts = ___,
         # use the lag counts and the cumulative counts to calculate the daily counts
         # hint: Look closely at the cumulative counts and the lagged values.
         daily = ___,
         # use the same approach to compute the daily recovered counts,
         lag_recovered = ___,
         daily_recovered = ___)


```

## (c) Plot the daily counts these for Victoria

```{r plot-daily-counts-student-copy}
# only plot the daily counts each day for victoria
# (write your own code for this)
```


# 5. (3pts) Use your internet search skills. What happened in Victoria that led to the spike in numbers in the first few days of May.  Post a link to where you found your information


!> Answer: ...
  

# 6. (2pts) If we want to compare the COVID-19 incidence across states, what is a limitation to only comparing the counts?


!> Answer: ...

# 7. (3pts) Join the count data with the state population data, and compute the COVID-19 incidence rate per 100,000 people. What state has the highest incidence rate?

```{r join-count-incidence-rate-student-copy}
state_pop <-tibble(
    state = c("NSW", "VIC", "QLD", "SA", "WA", "TAS", "NT", "ACT", "DP"),
    pop = c(8089526,6594804,5095100,1751693,2621680,426709,245869,420379, NA))

# join the covid data with state population data
oz_covid19_state <- ___

# compute the COVID-19 incidence rate per 100,000 people. 
oz_covid19_state_rate <- ___ %>%
  mutate(rate = ___)

# What state has the highest incidence rate?
oz_covid19_state_rate %>% arrange(___)
```

!> Answer: 

# 8. (2pts) Compute the COVID-19 testing rate per 1,000 people. Which state has the best (highest) testing performance?

```{r state-test-rate-student-copy}
oz_covid19_state_test_rate <- oz_covid19_state %>%
  # calculate the testing rate per 1,000 people. 
  mutate(test_rate = )

# Which state has the best (highest) testing performance?
oz_covid19_state_test_rate 
```

!> Answer: 

# 9. (4pts) Compute 7 day average of daily counts and recovery for Australia. What do we learn about the trajectory of the pandemic in Australia?

```{r q9-ozcovid-weekly-student-copy}
oz_covid_weekly <- oz_covid19_daily %>% 
  # step one, add weekly information using a function from lubridate
  mutate(week = ___) %>% 
  # For each of the weeks calculate the average for daily counts and daily recovered
  ___ %>% 
  # 
  summarise(mean_daily_count ___,
            ___)

# create a plot of the weekly average cases
ggplot(___,
       aes(x = ___,
           y = ___)) +
  geom_line()
  
# create a plot of the weekly average recovered?
ggplot(___) + 
  ___

```

!> Answer: What are some things you learn from the plot?

# 10. (2pts) From the data, what is the total number of cases and number of recovered cases for each state?

Calculate the total number of cases and number of recovered cases for each state. 

```{r covid_-state-totals-student-copy}
oz_covid_state_totals <- oz_covid19_daily %>% 
# calculate the total counts of cases and recovered per state
  # there are likely multiple steps here
  ___
```

!> Answer: 

# 11. (3pts) Plot a map of the proportion of recovered cases.

Read in the map file and join the state counts to the map data

```{r state-join-counts-student-copy}
library(sf)
# read in the map file, oz_map.rds
oz_map <- read_rds(___)

# join the state totals data onto the oz_map data
oz_shape_totals <- ___ %>% 
# hint: remember to check what you are joining the columns by
  left_join(___) %>% 
  # compute the proportion of recovered
  mutate(proportion_recovered = )
```

```{r plot-state-join-counts-student-copy}
ggplot(___,
       aes(x = ___,
           y = latitude,
           fill = ___)) + 
  geom_sf() + 
  scale_fill_viridis_c()

```

!> Answer: What do you learn from this plot?  

# 12. (4 pts) Across all of Australia, plot the daily cases against the cumulative cases and interpret the graphic, what do we learn?

```{r oz-covid19-daily-total-student-copy}
oz_covid19_daily_total <-  oz_covid19_daily %>% 
# Calculate the total cumulative cases for each day, and the
  # daily number of cases across all states for each day
  ___ %>% 
  ___
```

```{r plot-oz-covid19-daily-total-student-copy}
ggplot(oz_covid19_daily_total,
       aes(x = ___,
           y = ___)) + 
  geom_line() +
  scale_x_log10() + 
  scale_y_log10()
```

!> Answer: What do you learn from this plot?
